---
title: "merge_files"
output: html_document
date: "2023-02-20"
---

# Merge all the time aggregated files

Importing the libraries
```{r}
library(dplyr)
library(tidyr)
```

Read in the data files using the read.csv() or read.table() function. Make sure to specify the header = TRUE argument to indicate that the first row contains variable names.

```{r }
data1 =read.csv(file.choose(),header=T)
data2 =read.csv(file.choose(),header=T)
data3 =read.csv(file.choose(),header=T)
```

Combine the data files into one dataframe using the bind_rows() function from the dplyr package. This function will stack the data frames on top of each other, assuming that they have the same variable names.

```{r }
all_data = bind_rows(data1, data2, data3)
```

Use the unite() function from the tidyr package to combine the Date and Time columns into a single column called DateTime. This is necessary in order to properly order the time series data.

```{r }
all_data = all_data %>%
  unite(TurbineName, TimeStamp, Date, sep = " ")
```

Use the arrange() function from the dplyr package to sort the rows of the dataframe by Turbine ID and DateTime.
```{r }
all_data = all_data %>%
  arrange(Turbine.ID, DateTime)
```


```{r }

```
