---
title: "dataframes_aggregation"
output: html_document
date: "2023-02-22"
---

# Clean environment

```{r}
rm(list=ls())
```

## Importing library for the right_join

```{r}
library(dplyr)
```

## Importing the Windspeed, Generator and Fault Codes Dataframes

I am importing all the dataframes that I will join and also the dataframe called ims_and_oil which a team mate shared and later would become the master file with all the aggregated data

```{r}
All_windspeed_agg_1 = read.csv(file.choose(),header=T)
All_generator_rpm_agg_1 = read.csv(file.choose(),header=T)
All_fault_codes_agg_1 = read.csv(file.choose(),header=T)
```

## Rename my teammate's column to make it look like mine for ease in later join
```{r}
ims_and_oil_agg_1  = read.csv(file.choose(),header=T)
colnames(ims_and_oil_agg_1)[2] <- "interval_time"
```

## Checking for null values in all dataframes
```{r}
is.null(All_windspeed_agg_1)     #[1] FALSE
is.null(All_generator_rpm_agg_1) #[1] FALSE
is.null(All_fault_codes_agg_1)   #[1] FALSE
is.null(ims_and_oil_agg_1)     #[1] FALSE
```

## Merging all data frames with by matching two primary keys

Merging the Windspeed, Generator and Fault Codes Dataframes using the primary keys of: TurbineName and interval_time that both share

```{r}
wind_generator = full_join(All_windspeed_agg_1,All_generator_rpm_agg_1, by = c('TurbineName'='TurbineName', 'interval_time'='interval_time'))

is.null(wind_generator) #[1] FALSE

ims_wind_generator = full_join(wind_generator,ims_and_oil_agg_1, by = c('TurbineName'='TurbineName', 'interval_time'='interval_time'))

is.null(ims_wind_generator) #[1] FALSE
```



```{r}
new_data = right_join(merged_data,All_fault_codes, by = c('TurbineName'='TurbineName', 'interval_time'='interval_time'))
```

## Dropping the not-wanted columns

I am only interested in joining the numerical columns of my dataframes to the master file, so I will drop the following chategorical columns:

TimeStamp.x
Date.x 
MetricName.x 
TimeStamp.y 
Date.y 
MetricName.y

```{r}
drop_column = subset(new_data, select = -c(TimeStamp.x,Date.x,MetricName.x,TimeStamp.y,Date.y,MetricName.y))
```


## Adding my teammate column's to the master_data file
```{r}
master_data = right_join(ims_and_oil_1,drop_column, by = c('TurbineName'='TurbineName', 'interval_time'='interval_time'))
```

## Code Sources: 

 - How to merge dataframes by join: https://www.youtube.com/watch?v=jsxwF69wYaE.  



